### 2010-09-25 paper/IIWAS2010/content/results_discussion.tex
final after working with Pete

First, we built an ontology for the vehicular realm exploiting the Wikipedia pages, DBpedia categories, and WordNet synsets. For each of the classes in the ontology we built corpora from the corresponding Wikipedia pages. Figure \ref{fig:vehicular_ontology} shows a subsection of this ontology.

In Table \ref{tbl:nlp_engine_parse} we show the data that is output by the Morpheus NLP engines parse of the query.  It extracts the \emph{wh}-term that identifies the sentence as a question, identifies the answer class, and locates descriptive phrases that can be used to identify the answer. Finally, the engine produces n-grams from the phrases in the descriptive information sections.

Using the data in Table \ref{tbl:nlp_engine_parse} we determine relevant classes in non-increasing order of relevance. Table \ref{tbl:term_classes} shows the top classes and their probabilities for automotive queries.

\begin{table}[!]\footnotesize
	\begin{tabular}{|l|p{4.9cm}|}
		\hline 
		\emph{wh}-term & what \\
		\hline 
		descriptive phrases & \small 1997 Toyota Camry V6 \\
		\hline 
		asking for & size tires \\
		\hline 
		n-grams & \small 1997, 1997 Toyota, 1997 Toyota Camry, Toyota, Toyota Camry, Toyota Camry V6, Camry, Camry V6, V6 \\
		\hline
	\end{tabular}
	\caption{The output of NLP engine parse}
	\label{tbl:nlp_engine_parse} 
\end{table}

@@

\caption{Terms' top classes and probabilities}
\label{tbl:term_classes}

@@

We found the top class of the terms in the candidate SSQ and determined the class divergence with the qualified SSQ classes in the QRM store. Then, we combined the divergence measure and ranked QRMs based on the relevance score. Table \ref{tbl:ranked_queries} shows the top ranked SSQ for the query. Finally, we execute the best QRMs and display the results to the user.

@@

\caption{Top ranked queries}
\label{tbl:ranked_queries}

@@

In this paper, we propose a novel question answering system that uses the deep web and previously answered user queries to answer similar questions. The system uses a path finder to annotate answer paths so path followers can discover answers to similar questions.  Each (\emph{question, answer path}) pair is assigned a realm, and new questions are matched to existing (\emph{question, answer path}) pairs. Classification of new question terms into classes is based on term frequency distributions in our realm specific corpora of web documents.  These terms are the input to existing answer paths and we re-execute these paths with the new input to produce results.

%Manually forming a corpus of Wikipedia pages associated with a class is a cumbersome task. 
Topic modeling provides a promising approach to identifying pages relevant to a given class in a more automated manner. We believe a mix between our web form entry annotation methods and form label extraction \cite{1453931} can yield promising results. Combining this with the method of Elmeleegy et al. \cite{1687749} may completely remove the user from the answer path generation process.

Additionally, we are investigating methods of merging QRMs to answer compound questions.  We will also chain QRMs using the principles of transform composition \cite{transformscout}.

>>>>

First, we built an ontology for the vehicular realm exploiting the Wikipedia pages, DBpedia categories, and WordNet synsets. For each of the classes in the ontology we built corpora from the corresponding pWikipedia pages. Figure \ref{fig:vehicular_ontology} shows a subsection of this ontology.

In Table \ref{tbl:nlp_engine_parse} we show the data output by the Morpheus parse of the query.  It extracts the \emph{wh}-term that classifies the sentence as a question, identifies the answer class, and locates descriptive phrases to produce the answer. Finally, the engine produces n-grams from phrases in the descriptive information sections.

Using the data in Table \ref{tbl:nlp_engine_parse} we determine relevant classes in non-increasing order of relevance. Table \ref{tbl:term_classes} shows the eight best term classes and their probabilities for automotive queries.

\begin{table}[!]\footnotesize
	\begin{tabular}{|l|p{4.9cm}|}
		\hline 
		\emph{wh}-term & what \\
		\hline 
		descriptive phrases & \small 1997 Toyota Camry V6 \\
		\hline 
		asking for & size tires \\
		\hline 
		n-grams & \small 1997, 1997 Toyota, 1997 Toyota Camry, Toyota, Toyota Camry, Toyota Camry V6, Camry, Camry V6, V6 \\
		\hline
	\end{tabular}
	\caption{The output of NLP engine}
	\label{tbl:nlp_engine_parse} 
\end{table}

@@

\caption{Term classes and probabilities}
\label{tbl:term_classes}

@@

We found the best classes for the terms in the candidate SSQ. We calculated the class divergence between these classes and the qualified SSQ classes in the QRM store. QRMs are ranked based upon the relevance score and the class divergence measure. Table \ref{tbl:ranked_queries} shows the thAnswers are produced by the QRE, a python back end.ree highest ranked queries. Finally, we execute the best QRMs and display the results to the user.

@@

\caption{Highest ranked queries}
\label{tbl:ranked_queries}

@@

In this paper, we propose a novel question answering system that uses the deep web and previously answered user queries to answer similar questions. The system uses a path finder to annotate answer paths so path followers can discover answers to similar questions.  Each (\emph{question, answer path}) pair is assigned a realm, and new questions are matched to existing (\emph{question, answer path}) pairs. The classification of new question terms into classes is based on term frequency distributions in our realm specific corpora of web documents.  These terms are the input to existing answer paths and we re-execute these paths with the new input to produce answers.

Our solution is composed a web front end where users can ask questions. The QRR was developed as a Firefox plugin and an associated C\# application.  Our similarity measures were coded using Java and open source libraries. Answers are produced by the QRE, a python back end. The data is stored in a PostresSQL database.

%Manually forming a corpus of Wikipedia pages associated with a class is a cumbersome task. 
Topic modeling provides a promising approach to identifying pages relevant to a class in a more automated manner. We believe our web form entry annotation methods and form label extraction \cite{1453931} can yield promising results. Combining this with the method of Elmeleegy et al. \cite{1687749} may remove the user from the answer path generation process.

Additionally, we are investigating methods of merging QRMs to answer compound questions.  This will allow us to chain QRMs using the principles of transform composition \cite{transformscout}.

### 2010-09-25 paper/IIWAS2010/content/system_arch.tex
final after working with Pete

Note, if $S \prec T$ and $S \not\prec Q$ then $cd(S,T) < cd(S,Q)$, that is, the divergence of a source class to a target ancestor class is smaller than the divergence of a source class to any class that is not an ancestor. This is an important property in determining the compatibility of classes for answering queries.  If an SSQ answers queries concerning an ancestor class, it is more relevant than an SSQ that answers queries from any non-ancestral class.

Suppose we want to find the class divergence between \emph{Bus} and \emph{Sedan} from the ontology shown in Figure \ref{fig:vehicular_ontology}. \emph{Sedan} is a subclass of \emph{Automobile} which is a subclass of \emph{Land\_Vehicle}.  \emph{Bus} is a subclass of \emph{Land\_Vehicle}, which is their least common ancestor $C$.

The longest path to the tree root is $h = 4$. Therefore, the normalized divergence $cd(Bus, Sedan) = 6/12$. The value is calculated from $d(Bus, Root) = 3$, $d(Bus, Land\_Vehicle) = 1$, and $d(Sedan, Land\_Vehicle) = 2$.

@@

Once we have ranked the QRMs for a given user query, we can produce answers by re-running the pathways stored in the QRMs. The Morpheus \emph{Query Executor} (QE) evaluates a script of the query resolving process.  It simulates a human clicking buttons to follow links, submitting forms, and highlighting of data to form a textual answer.  The QE assumes that because of the auto generated nature of deep web pages, the location of answers are the same irrespective of page changes.  It uses the relative XPath location to the answer node on HTML pages as described in \cite{Badica06}.

>>>>

Note, if $S \prec T$ and $S \not\prec Q$ then $cd(S,T) < cd(S,Q)$, that is, the divergence of a source class to a target ancestor class is smaller than the divergence of a source class to any class that is not an ancestor. This is an important property in determining the compatibility of classes for answering queries.  If an SSQ answers queries concerning an ancestor class, it is more relevant than an SSQ that anwers queries from any non-ancestral class.

Suppose we want to find the class divergence between \emph{Bus} and \emph{Sedan} from the ontology shown in Figure \ref{fig:vehicular_ontology}. \emph{Land\_Vehicle} is their least common ancestor because \emph{Sedan} is a subclass of \emph{Automobile}, which is a subclass of \emph{Land\_Vehicle}, and \emph{Bus} is a subclass of \emph{Land\_Vehicle}.

The longest path from \emph{Bus} and \emph{sedan} to the tree root is four ($h = 4$). By formula \ref{eq:cd}, $cd(Bus, Sedan)$ = $( d(Bus, Root)$ + $d(Bus, Land\_Vehicle)$ + $d(Sedan, Land\_Vehicle)) / (3h)$ thus $(3 + 1 + 2) / (3 * 4) = 6/12$.

@@

Once we have ranked the QRMs for a given user query, we can produce answers by re-visiting the pathways stored in the QRMs. The Morpheus \emph{Query Executor} (QE) evaluates a script of the query resolving process.  It simulates a human clicking buttons to follow links, submit forms, and highlight data, forming a textual answer.  The QE assumes that because of the auto generated nature of deep web pages, the location of answers are the same irrespective of page changes.  It uses the relative XPath location to the answer node on HTML pages as described in \cite{Badica06}.
